---
title: "Loading BIP applications"
output: html_document
header-includes:
  - \usepackage{color}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE )
library(leaflet)
library(sf)
library(magrittr)
library(dplyr)
```

Load Data

```{r loadingdata}
approved_dbf <- foreign::read.dbf("~/git/rural_broadband/data/rus_broadband_servicearea/RD_BB_ApprovedSA.dbf")

bip_awardees <- readxl::read_excel("~/git/rural_broadband/data/rus_telecom_program/BIP_R1-R2AwardeeMaster_10-29-10_updNetObl_7-3-19.xlsx", 
                                   sheet = "Infrastructure", 
                                   col_types = c("text", "text", "text", "text", "text", "text", "text", "date", 
                                                 "text", "text", "text", "text", "text", "text", "text", "text", 
                                                 "text", "text", "text", "text", "text", "text", "text", "text", 
                                                 "text", "numeric", "numeric", "numeric", "numeric", "numeric", 
                                                 "text", "numeric", "numeric", "numeric", "text", "text", "text", 
                                                 "text", "text", "numeric", "numeric", "numeric", "numeric", 
                                                 "numeric", "numeric", "numeric", "text"))
```

RUS Shapefile columns

took 2 rows (out of 8) from DC1101 application in VA 

```{r}
approved_dbf %>% filter(RUS_ID == "DC1101") %>% head(2) %>% knitr::kable()

approved_dbf %>% filter(RUS_ID == "DC1101") %>% head(2) 
```

RUS Awardees columns

```{r}
bip_awardees2 <- bip_awardees %>% filter(`RUS Award No.` == "DC1101")
colnames(bip_awardees2) <- stringr::str_remove_all(colnames(bip_awardees), "[:space:]|[:punct:]") 
bip_awardees2 %>% knitr::kable()


```

Things that look in common: 

RUS Shapefile | RUS Awardee                |Match notes
--------------|----------------------------|-------------
RUS_ID        | RUS Award No.              | exact match
PUBLISHEDD    | Obligation Date            | lag ? 
SERVICETYP    | Technology Type (7 fields) | fuzzy match


Assumptions

RUS Shapefile: 
 
* STATUS/APPSTATUSS - assuming everything in awardee file is approved
* PROGRAMTYP - see below but assuming that LM and MM programs in awardees are BIP

## Thinking about Joins

#### Map Reference Number

Looking at Map Reference Number (Awardees) and Reference Number (Shape files)

Virginia applications in shapefiles do not have any Reference Numbers

```{r}
VA_RUSID <- c("DC1101", "NC1104", "VA1112", "WI1117")
bip_awardees %>% filter(`RUS Award No.` %in% VA_RUSID) %>% select(`Map Reference Number`)
approved_dbf %>% filter(RUS_ID %in% VA_RUSID)  %>% select(REFNUMBER) %>% distinct()
```

Are there any filled in Reference Numbers? (Shapefile)

Are any of those in the Map Reference Numbers (Awardees)
(1 is - MO1104 by Ralls County Electric Cooperative in Missouri)

```{r}
shapefile_refnumbers <- approved_dbf %>% filter(!is.na(REFNUMBER)) 
bip_awardees %>% filter(`Map Reference Number` %in% shapefile_refnumbers$REFNUMBER) %>% select(1:5) %>% knitr::kable()
```

```{r}
bip_awardees %>% inner_join(shapefile_refnumbers, by = c("Map Reference Number" = "REFNUMBER")) %>% select(1:5) %>% knitr::kable()
```

#### RUS ID

Collapsed Merge

```{r}
collapsedshape <- approved_dbf %>% select(RUS_ID, COMPANY, PROGRAMTYP, PROGRAMSER, REFNUMBER) %>% distinct() # goes from 1557 to 320
collapsed_awardees <- bip_awardees %>% select(`RUS Award No.`, `Recipient Name`, `Project Type (Simplified)`, `Map Reference Number`) %>% distinct() # goes from 301 to 299

collapsed_merge <- inner_join(collapsedshape, collapsed_awardees, by = c("RUS_ID" = "RUS Award No."))
```

X by Company - seems to match across sets

```{r}
collapsed_merge %>% select(COMPANY, `Recipient Name`) %>% head(15) %>% knitr::kable()
```

X by Program - not matching!

This explains discrepancy - what I received, the program service 
sometimes specifies 'middle mile' or 'last mile' and I wasn't sure if these were technically BIP, but they appear in the BIP awardee file
```{r}
collapsed_merge %>% select(PROGRAMTYP, PROGRAMSER, `Project Type (Simplified)`) %>% distinct() %>% knitr::kable()
```

How many missed?

```{r}
merge_progcombination_count <- collapsed_merge %>% group_by(RUS_ID, PROGRAMTYP, PROGRAMSER, `Project Type (Simplified)`) %>% summarise(rows = n()) %>% select(-rows) %>% group_by(PROGRAMTYP, PROGRAMSER, `Project Type (Simplified)`) %>% summarise(RUSID_count = n())

split(merge_progcombination_count, merge_progcombination_count$`Project Type (Simplified)`)
```


X by Map Reference Number - nothing to match

only 4 Ref numbers on shape file at all and only 1 of these that carries over to Map Reference Number 

```{r}
collapsed_merge %>% select(REFNUMBER, `Map Reference Number`) %>% distinct() %>% filter(!is.na(REFNUMBER)) %>% knitr::kable()
```


```{r}
approved_shapes <- approved_dbf %>% select(RUS_ID, SHAPE_Area) %>% distinct()
bip_awards <- bip_awardees[,c(3,7,9)] %>% distinct()


multrus_awardees <- bip_awardees %>% group_by(`RUS Award No.`) %>% summarise(n = n()) %>% filter(n > 1) %>% select(`RUS Award No.`)
multrus_awardees <- unique(multrus_awardees$`RUS Award No.`)

bip_awardees %>% filter(`RUS Award No.` %in% multrus_awardees) %>% arrange(`RUS Award No.`) %>% select(-`App ID`, -`NOFA Round`, -`Awardee ID`, -`BAIL ID`) 

bip_awardees %>% filter(`RUS Award No.` %in% multrus_awardees) %>% arrange(`RUS Award No.`) %>% distinct()

length(unique(bip_awardees$`Map Reference Number`))
table(approved_dbf$REFNUMBER)

length(setdiff(unique(approved_shapes$RUS_ID), unique(bip_awards$`RUS Award No.`)))
length(union(unique(approved_shapes$RUS_ID), unique(bip_awards$`RUS Award No.`)))

approved_shapes %>% select(RUS_ID) %>% distinct() %>% 
  inner_join(bip_awards %>% select(`RUS Award No.`) %>% distinct(), by = c("RUS_ID" = "RUS Award No."))

approved_shapes %>% select(RUS_ID) %>% distinct() %>% 
  anti_join(bip_awards  %>% select(`RUS Award No.`) %>% distinct(), by = c("RUS_ID" = "RUS Award No."))

52+229

bip_awardees  %>% 
  inner_join(approved_shapes, by = c("RUS Award No." = "RUS_ID")) %>% 
  filter(stringr::str_detect(`States Served`, "VA") == TRUE)
  filter(`RUS Award No.` %in% VA_RUSID)

bip_awards %>% select(`RUS Award No.`) %>% distinct() %>% 
  anti_join(approved_shapes %>% select(RUS_ID) %>% distinct(), by = c("RUS Award No." = "RUS_ID"))

220 + 29

```




